On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-07 AvdMomZvol_rails/Article.tex
[AMZr] A ref to existent rails sets

Among the rails sets, sets with 2 points on one line and all the other on another line prevail.

>>>>

Among the rails sets, sets with 2 points on one line and all the other on another line prevail.
In Section~\ref{sec:bounds_rails} below, some examples of such sets are discussed;
they include an example of rails sets with 2 points on one line and 38 point on the other line
(Fig.~\ref{picture_40.png})
and
an example of rails set with 4 points on one line and 4 points on the other
(Fig.~\ref{picture.png}).
We have no examples of rails set with 4 points on one line and 5 points on the other;
and we have no examples of rails sets with 3 points on one line and 9 points on the other.
